Bird beak's elaboration and innovation

### 2023-05-25 Analysis/04-Figure_with_ellipse_phyloview.Rmd
rename

## Non coloured version
grey.palette <- function(n) {return(rep("grey", n))}
tip_colours_orders <- plot.short.tree(tree, shapespace, "level2", tip.order = tip_order, colour.palette = black.palette)
tip_colours_orders[1:length(tip_colours_orders)] <- "black"

@@

## Black version
tip_colours_super_orders[1:length(tip_colours_super_orders)] <- "black"
## Grey version
# tip_colours_super_orders <- rep("darkgrey", length(tip_colours_super_orders))

>>>>

## Non coloured version
grey.palette <- function(n) {return(rep("grey", n))}
tip_colours_orders <- plot.short.tree(tree, shapespace, "level2", tip.order = tip_order, colour.palette = grey.palette)
tip_colours_orders[1:length(tip_colours_orders)] <- "#191919"

@@

## Black version
tip_colours_super_orders[1:length(tip_colours_super_orders)] <- "#191919"
## Grey version
# tip_colours_super_orders <- rep("#191919", length(tip_colours_super_orders))
